---
title: "WNBA"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: 
      bootswatch: flatly
---

About
==========================


### **Additional Information:** 

**Authors:**

Belle Schmidt, Liam Jennings, and Cole Siniawski


**Objective:**

Although we outlined a few questions, our shiny app gives viewers the flexibility to look at many different questions regarding the WNBA. We hope that viewers may be able to learn more about the best teams and players and be able to find similarities and differences between the best and the worst.


**Tribulations and Victories of Data Acquisition and Wrangling:**




**Color Scheme:**




### **Defining The Variables**

```{r global, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(flexdashboard)
library(wehoop)
library(paletteer)
library(shiny)
library(bslib)
library(patchwork)
library(sportyR)
library(stringr)
theme_set(theme_bw())

wnba_shots <- read_csv("https://raw.githubusercontent.com/36-SURE/36-SURE.github.io/main/data/wnba_shots.csv")

#View(wnba_shots)
```


```{r, echo = FALSE}
wnba_shots <- wnba_shots |>
  # Removes all star games
  filter(shooting_team != "Team Stewart" & shooting_team != "Team Wilson") |> 
  # Identified which player shot the ball
   mutate(
     shooting_player = ifelse(str_detect(desc, "blocks") == TRUE,               sub(".*?\\b(?:blocks)\\W+(\\w+(?:\\W+\\w+){0,2})\\b(?:'s| 's| B. 's)\\s.*", "\\1", desc, perl = TRUE), sub("\\ makes.*|\\ misses.*|\\ B. makes.*|\\ B. misses.*", "\\1", desc)), 
      # Determines score differential after each shot
      score_differential = home_score - away_score, 
      # Determines which free throw number it was
      free_throw = if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 3 of"), 3, if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 2 of"), 2, if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 1 of") | str_detect(shot_type, "[Tt]echnical"), 1, 0))), 
       made_shot = if_else(made_shot == "TRUE", "Made", "Missed"),  
      #Determines if the shooting team was home or away
       Shooting_Team_Home_Away = if_else(shooting_team == home_team_name, "Home", "Away"),
       coordinate_x = abs(coordinate_x),   
      # Rename shooting_team to include team name and city 
      shooting_team = case_match(
      shooting_team,
      "Atlanta" ~ "Atlanta Dream",
      "Chicago" ~ "Chicago Sky",
      "Connecticut" ~ "Connecticut Sun",
      "Dallas" ~ "Dallas Wings",
      "Indiana" ~ "Indiana Fever",
      "Las Vegas" ~ "Las Vegas Aces",
      "Los Angeles" ~ "Los Angeles Spark",
      "Minnesota" ~ "Minnesota Lynx",
      "New York" ~ "New York Liberty",
      "Phoenix" ~ "Phoenix Mercury",
      "Seattle" ~ "Seattle Storm",
      "Washington" ~ "Washington Mystics"
    ),
    home_team_name = case_match(
      home_team_name,
      "Atlanta" ~ "Atlanta Dream",
      "Chicago" ~ "Chicago Sky",
      "Connecticut" ~ "Connecticut Sun",
      "Dallas" ~ "Dallas Wings",
      "Indiana" ~ "Indiana Fever",
      "Las Vegas" ~ "Las Vegas Aces",
      "Los Angeles" ~ "Los Angeles Spark",
      "Minnesota" ~ "Minnesota Lynx",
      "New York" ~ "New York Liberty",
      "Phoenix" ~ "Phoenix Mercury",
      "Seattle" ~ "Seattle Storm",
      "Washington" ~ "Washington Mystics"),
    away_team_name = case_match(
      away_team_name,
      "Atlanta" ~ "Atlanta Dream",
      "Chicago" ~ "Chicago Sky",
      "Connecticut" ~ "Connecticut Sun",
      "Dallas" ~ "Dallas Wings",
      "Indiana" ~ "Indiana Fever",
      "Las Vegas" ~ "Las Vegas Aces",
      "Los Angeles" ~ "Los Angeles Spark",
      "Minnesota" ~ "Minnesota Lynx",
      "New York" ~ "New York Liberty",
      "Phoenix" ~ "Phoenix Mercury",
      "Seattle" ~ "Seattle Storm",
      "Washington" ~ "Washington Mystics"))

  
  

#View(wnba_shots)
```

```{r, echo = FALSE}
# Shots taken in the last 30 seconds of the fourth quarter where the score differential was less than 6 after the shot was taken
end_of_game_shots <- wnba_shots |>
  filter(game_seconds_remaining <= 30 & score_differential %in% c(-6, -5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6) & qtr == 4) 

# All close games
all_close_games <- end_of_game_shots|> 
  distinct(game_id) 

# All shots taken in last 30 seconds 
all_shots <- wnba_shots|>
  filter(game_seconds_remaining <= 30 & qtr == 4) 
  
# All shots taken in last 30 seconds in close games
all_close_game_shots <- left_join(all_close_games, all_shots) |> 
  mutate(made_shot = factor(made_shot,levels = c("Missed", "Made"))) |> 
  arrange(shooting_team)

# The earliest time within the last 30 seconds where a shot occurred for a close game
close_games <- end_of_game_shots |> 
  group_by(game_id) |> 
  slice_max(game_seconds_remaining) |> 
  arrange(-free_throw) |> 
  slice_head() |> 
  select(game_id, home_team_name, away_team_name, score_differential) 


# The score after the last shot of every game 
final_score <- wnba_shots |> 
  group_by(game_id) |> 
  slice_min(game_seconds_remaining) |> 
  arrange(free_throw) |> 
  slice_head() |> 
   rename(final_score_differential = score_differential) |> 
   select(game_id, final_score_differential) 

# Score change from first shot in last 30 seconds to last shot of game & final outcomes added
close_games_observing <- left_join(close_games, final_score) |> 
  mutate(home_team_outcome =  
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential == final_score_differential, "Won - Kept Same Lead",
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential > final_score_differential, "Won - Lead Decreased",
 if_else(score_differential > 0 & final_score_differential > 0, "Won - Extended Lead",
 if_else(score_differential > 0 & final_score_differential == 0, "Tied - Lost Lead", 
 if_else(score_differential > 0 & final_score_differential < 0, "Lost - Lost Lead", 
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential == final_score_differential, "Lost - No Comeback",
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential > final_score_differential, "Lost - Deficit Increased",
 if_else(score_differential < 0 & final_score_differential < 0 & final_score_differential > score_differential, "Lost - Deficit Decreased",
 if_else(score_differential < 0 & final_score_differential == 0, "Tied - Comeback",
 if_else(score_differential == 0 & final_score_differential == 0, "Tied - No Change",
 if_else(score_differential == 0 & final_score_differential > 0, "Won - From Tie",
 if_else(score_differential == 0 & final_score_differential < 0, "Lost - From Tie", 
         "Won - Took Lead From Loss")))))))))))),
 away_team_outcome =  
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential == final_score_differential, "Lost - No Comeback",
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential > final_score_differential, "Lost - Deficit Decreased",
 if_else(score_differential > 0 & final_score_differential > 0, "Lost - Deficit Increased",
 if_else(score_differential > 0 & final_score_differential == 0, "Tied - Comeback", 
 if_else(score_differential > 0 & final_score_differential < 0, "Won - Took Lead From Loss", 
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential == final_score_differential, "Won - Kept Same Lead",
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential > final_score_differential, "Won - Extended Lead",
 if_else(score_differential < 0 & final_score_differential < 0 & final_score_differential > score_differential, "Won - Lead Decreased",
 if_else(score_differential < 0 & final_score_differential == 0, "Tied - Lost Lead",
 if_else(score_differential == 0 & final_score_differential == 0, "Tied - No Change",
 if_else(score_differential == 0 & final_score_differential > 0, "Lost - From Tie",
 if_else(score_differential == 0 & final_score_differential < 0, "Won - From Tie", 
         "Lost - Lost Lead")))))))))))),
 Home_Result = if_else(str_detect(home_team_outcome, "^Won"), "Win",
                       if_else(str_detect(home_team_outcome, "^Lost"), "Loss", "Tie")),
         Away_Result = if_else(str_detect(away_team_outcome, "^Won"), "Win",
                       if_else(str_detect(away_team_outcome, "^Lost"), "Loss", "Tie")))|> 
  ungroup() |> 
  mutate(away_team_outcome = factor(away_team_outcome, levels = c("Lost - Lost Lead", "Lost - Deficit Increased", "Lost - No Comeback", "Lost - Deficit Decreased", "Lost - From Tie", "Tied - Lost Lead", "Tied - No Change", "Tied - Comeback", "Won - Lead Decreased", "Won - Kept Same Lead", "Won - Extended Lead", "Won - From Tie", "Won - Took Lead From Loss")),
         home_team_outcome =factor(home_team_outcome, levels = c("Lost - Lost Lead", "Lost - Deficit Increased", "Lost - No Comeback", "Lost - Deficit Decreased", "Lost - From Tie", "Tied - Lost Lead", "Tied - No Change", "Tied - Comeback", "Won - Lead Decreased", "Won - Kept Same Lead", "Won - Extended Lead", "Won - From Tie", "Won - Took Lead From Loss")))



# Counts number of home close game wins and losses per team
home_win_loss <- close_games_observing |> 
  group_by(home_team_name, Home_Result) |> 
  summarise(num_times_home = n()) |> 
  rename(team = home_team_name,
         result = Home_Result)

# Counts number of away close game wins and losses per team
away_win_losses <- close_games_observing |> 
  group_by(away_team_name, Away_Result) |> 
  summarise(num_times_away = n()) |> 
  rename(team = away_team_name,
         result = Away_Result)

# Combines both away and home wins and losses in close games 
win_loss_per_team <- full_join(away_win_losses, home_win_loss) |> 
 mutate(num_times_home = replace_na(num_times_home, 0),
        num_times_away = replace_na(num_times_away, 0)) |> 
  pivot_longer(num_times_home:num_times_away,
               values_to = "occurences",
               names_to = "home_or_away") |> 
  mutate(home_or_away = ifelse(home_or_away == "num_times_home", "Home", "Away"),
         result = factor(result, levels = c("Loss", "Tie", "Win"))) |> 
  ungroup() 


# Both away and home wins vs. losses for entire league
win_losses <- close_games_observing |>
  pivot_longer(Home_Result:Away_Result,
               values_to = "win_or_loss",
               names_to = "home_or_away_result") |> 
  mutate(home_or_away_result = ifelse(home_or_away_result == "Home_Result", "Home", "Away"))
         
# Determines if team was home or away 
win_losses2 <- close_games_observing |>
  pivot_longer(home_team_name:away_team_name,
               values_to = "teams",
               names_to = "home_or_away_team") |> 
  mutate(home_or_away_team = ifelse(home_or_away_team == "home_team_name", "Home", "Away")) |> 
  arrange(teams)


# Home team outcome type for entire league
num_home_outcomes <- close_games_observing |>
  select(home_team_outcome, Home_Result) |> 
  count(home_team_outcome, Home_Result) |> 
  rename(num_times_home = n,
         outcome = home_team_outcome)

# Away team outcome for entire league
num_away_outcomes <- close_games_observing |>
  select(away_team_outcome, Away_Result) |> 
  count(away_team_outcome, Away_Result) |> 
  rename(num_times_away = n,
         outcome = away_team_outcome) 


# Number of occurrences for each outcome type during the season - both home vs. away 
possible_outcomes <- full_join(num_home_outcomes, num_away_outcomes, by = "outcome") |> 
  mutate(num_times_home = replace_na(num_times_home, 0),
         num_times_away = replace_na(num_times_away, 0),
         Win_Loss = ifelse(is.na(Away_Result), Home_Result, Away_Result)) |> 
  select(-Home_Result, -Away_Result)


# Number of times each outcome type occurred for each team while they were home
home_game_results <- close_games_observing |> 
  group_by(home_team_name, home_team_outcome, Home_Result) |>
  summarise(num_times_home_per_team = n()) |> 
  rename(outcome = home_team_outcome) |> 
  ungroup()


# Number of times each outcome type occurred for each team while they were away
away_game_results <- close_games_observing |> 
  group_by(away_team_name, away_team_outcome, Away_Result) |> 
  summarise(times_occured_away_per_team = n()) |> 
  rename(outcome = away_team_outcome) |> 
  ungroup()


# Number of shots made vs missed in league
all_shots_made <- all_close_game_shots |> 
  count(made_shot) 

all_shots_made$team <- c("Entire League", "Entire League")

#### Shot Cart Clean dataset
wnba_shot_chart <- wnba_shots |>
  # filter by regular season and remove outliers
  filter(game_type == 2 & abs(coordinate_x) >= 10 &
           # remove free throws 
           str_like(shot_type, "Free Throw%") == FALSE) |> 
  mutate(made_shot = if_else(made_shot == "Made", TRUE, FALSE))
  
# WNBA court (New York Liberty)
nyl_court <- sportyR::geom_basketball("WNBA", display = "offense", rotation = 90,
                                      color_updates = list(
                                        panel_background = "black",
                                        offensive_half_court = "gray",
                                        court_apron = "#6ECEB2",
                                        center_circle_outline = "white",
                                        center_circle_fill = "#6ECEB2",
                                        endline = "white",
                                        sideline = "white",
                                        division_line = "white",
                                        two_point_range = "#857e82",
                                        painted_area = "#2a2729",
                                        lane_boundary = "white",
                                        free_throw_circle_fill = "#857e82",
                                        inbounding_line = "white",
                                        substitution_line = "white",
                                        three_point_line = "white",
                                        lane_space_mark = "white",
                                        free_throw_circle_outline = "#6ECEB2",
                                        free_throw_circle_dash = "#6ECEB2",
                                        baseline_lower_defensive_box = "white",
                                        lane_lower_defensive_box = "#6ECEB2",
                                        restricted_arc = "#6ECEB2"
                                      ))

# vector assigning color to each team 
color_vector <- c("Atlanta Dream" = "#C8102E", "Chicago Sky" = "#418FDE", "Connecticut Sun" = "#643335", "Dallas Wings" = "#C4D600", "Indiana Fever" = "#FFCD00", "Las Vegas Aces" = "#000000", "Los Angeles Spark" = "#702F8A", "Minnesota Lynx" = "#236192", "New York Liberty" = "#003DA5", "Phoenix Mercury" = "#CB6015", "Seattle Storm" = "#2C5234", "Washington Mystics" = "#0C2340")

# vector assigning color to each outcome type
win_loss_type_color_vector <- c("Lost - Lost Lead" = "firebrick4", "Lost - Deficit Increased" = "firebrick", "Lost - No Comeback" = "firebrick3", "Lost - Deficit Decreased" = "firebrick2", "Lost - From Tie" = "firebrick1", "Tied - Lost Lead" = "darkorange1", "Tied - No Change" = "goldenrod1", "Tied - Comeback" = "gold", "Won - Lead Decreased" = "lightgreen", "Won - Kept Same Lead" = "green1", "Won - Extended Lead" = "green3", "Won - From Tie" = "green4", "Won - Took Lead From Loss" = "darkgreen")


# Win, Tie, Loss Color Assignment 
win_loss_color_vector <- c("firebrick", "goldenrod1", "green4")

names(win_loss_color_vector) <- levels(win_loss_per_team$result)


custom_color <- scale_fill_manual(name = "Result", values = win_loss_color_vector)

```



Wins and Losses in Close Home Games vs Close Away Games
=============================================================

### Overarching Question 2 - How Do Each Of The Teams Perform In Close Home Compared To Close Away Games? How does that compare to the league average?


Inputs {.sidebar}
-------------------------

```{r, echo=FALSE}
  
  inputPanel(
 selectInput("teams5", label = "Team:", 
             choices = c("Atlanta Dream" = "Atlanta Dream",
                         "Chicago Sky" = "Chicago Sky",
                         "Connecticut Sun" = "Connecticut Sun",
                         "Dallas Wings" = "Dallas Wings",
                         "Indiana Fever" = "Indiana Fever",
                         "Las Vegas Aces" = "Las Vegas Aces",
                         "Los Angeles Spark" = "Los Angeles Spark",
                         "Minnesota Lynx" = "Minnesota Lynx",
                         "New York Liberty" = "New York Liberty",
                         "Phoenix Mercury" = "Phoenix Mercury",
                         "Seattle Storm" = "Seattle Storm",
                         "Washington Mystics" = "Washington Mystics"))
)
```

Row
-------------------------------------

```{r, echo=FALSE}
renderPlot({
ggplot(win_losses, aes(x = home_or_away_result, fill = win_or_loss)) +
  geom_bar(position = position_fill()) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  custom_color +
  labs(title = "Results Of Home And Away Teams In Close Games",
       x = "Home Or Away",
       fill = "Result")  +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 19),
          legend.title = element_text(face = "bold", size = 15),
          axis.title.y = element_blank(),
          axis.title.x = element_text(face = "bold", size = 15))
 }, height = 500, width = 605)

```


```{r, echo=FALSE}
renderPlot({
  
win_loss_per_team |> 
  filter(team == input$teams5) |>
  ggplot(aes(x = home_or_away, y = occurences, fill = result)) +
  geom_bar(position = position_fill(), stat = "identity") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  custom_color +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 19),
        legend.title = element_text(face = "bold", size = 15),
        axis.title.y = element_blank(),
        axis.title.x = element_text(face = "bold", size = 15)) +
  labs(title = paste(input$teams5, "Home vs. Away Close Game Results"), 
       x = "Home Or Away",
       fill = "Result") 
 }, height = 500, width = 605)
```

Row
-------------------------------------


```{r, echo=FALSE}

renderPlot({

  win_losses2 |> 
    filter(teams == input$teams5) |> 
    ggplot(aes(x = home_or_away_team, fill = home_or_away_team)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("#161616", "#B54213")) +
  theme(panel.background = element_rect(fill = "gray80"), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold", size = 15),
        legend.title = element_blank(),
        axis.title = element_text(face = "bold", size = 13),
        legend.position = "none") +
  labs(title = paste("Number of Close Home And Away Games The", input$teams5, "Played In"),
       y = "Number of Close Games",
       x = "Home Or Away") 
  }, height = 520, width = 605)

```



Outcome Types in Close Home Games vs Close Away Games
============================================================= 

Inputs {.sidebar}
-------------------------

```{r, echo=FALSE}

inputPanel(
 selectInput("teams2", label = "Away Team Graph:", 
             choices = c("Atlanta Dream" = "Atlanta Dream",
                         "Chicago Sky" = "Chicago Sky",
                         "Connecticut Sun" = "Connecticut Sun",
                         "Dallas Wings" = "Dallas Wings",
                         "Indiana Fever" = "Indiana Fever",
                         "Las Vegas Aces" = "Las Vegas Aces",
                         "Los Angeles Spark" = "Los Angeles Spark",
                         "Minnesota Lynx" = "Minnesota Lynx",
                         "Phoenix Mercury" = "Phoenix Mercury",
                         "Seattle Storm" = "Seattle Storm",
                         "Washington Mystics" = "Washington Mystics",
                         "New York Liberty" = "New York Liberty"))
)
```

```{r, echo=FALSE}

inputPanel(
 selectInput("teams1", label = "Home Team Graph:", 
             choices = c("Atlanta Dream" = "Atlanta Dream",
                         "Chicago Sky" = "Chicago Sky",
                         "Connecticut Sun" = "Connecticut Sun",
                         "Dallas Wings" = "Dallas Wings",
                         "Indiana Fever" = "Indiana Fever",
                         "Las Vegas Aces" = "Las Vegas Aces",
                         "Los Angeles Spark" = "Los Angeles Spark",
                         "Minnesota Lynx" = "Minnesota Lynx",
                         "Phoenix Mercury" = "Phoenix Mercury",
                         "Seattle Storm" = "Seattle Storm",
                         "Washington Mystics" = "Washington Mystics",
                         "New York Liberty" = "New York Liberty"))
)

```


Row
-------------------------------------  

```{r}
# Home Outcome Types Occured Across Leagues In Close Games
renderPlot({
  home_outcomes <- ggplot(possible_outcomes, aes(x = Win_Loss, y = num_times_home, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Times Each Outcome Type Occurred In Close Games For Home Teams",
       y = "Occurences",
       fill = "Outcome") +
  scale_fill_manual(values = win_loss_type_color_vector) +
  theme(axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
        legend.title = element_text(face = "bold")) 



# Away Outcome Types Occurred Across Leagues In Close Games
away_outcomes <- ggplot(possible_outcomes, aes(x = Win_Loss, y = num_times_away, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Times Each Outcome Type Occurred In Close Games For Away Teams",
       y = "Occurences",
       fill = "Outcome") +
  scale_fill_manual(values = win_loss_type_color_vector) +
  theme(axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold", size = 13),
        legend.title = element_text(face = "bold")) 


away_outcomes + home_outcomes +
  plot_layout(guides = "collect", nrow = 2)
}, height = 500, width = 605)
```


```{r, echo=FALSE}

renderPlot({
    # Plot for home outcomes
    filtered_teams2 <- if("All" %in% input$teams1) {
      home_game_results
    } else {
      home_game_results |>
        filter(home_team_name %in% input$teams1)
    }
    
    Team_home_outcomes <- ggplot(filtered_teams2, aes(x = Home_Result, y = num_times_home_per_team, fill = outcome)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = paste("Outcome Type In Close Games While The", input$teams1, "Was At Home"),
           y = "Occurences",
           fill = "Outcome") +
      scale_fill_manual(values = win_loss_type_color_vector) +
      theme(axis.title.x = element_blank(),
            plot.title = element_text(hjust = 0.5, face = "bold", size = 13),
            legend.title = element_text(face = "bold")) 

    # Plot for away outcomes
    filtered_teams3 <- if("All" %in% input$teams2) {
      away_game_results
    } else {
      away_game_results |>
        filter(away_team_name %in% input$teams2)
    }

    Team_away_outcomes <- ggplot(filtered_teams3, aes(x = Away_Result, y = times_occured_away_per_team, fill = outcome)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = paste("Outcome Type In Close Games While The", input$teams2, "Was Away"),
           y = "Occurences",
           fill = "Outcome") +
      scale_fill_manual(values = win_loss_type_color_vector) +
      theme(axis.title.x = element_blank(),
            plot.title = element_text(hjust = 0.5, face = "bold", size = 13),
            legend.title = element_text(face = "bold")) 

     Team_away_outcomes + Team_home_outcomes +
  plot_layout(guides = "collect", nrow = 2)
}, height = 500, width = 605)
```


Row
-------------------------

### **Question & Plots Explanation:**

**Question 1:** The first question we chose to look at is how the various audio features differ by genre. 



**Plots Explanation:** The left plot analyzes these features over time and the right plot measures the frequency of each feature by genre. The viewer has the ability to compare different genres and observe how the audio features have changed over time or compare the frequency of various audio features.


### **Observations / Conclusions:**

- For the majority of genres, danceability, loudness, and liveness have increased over time.

- For the majority of genres, energy, speechiness, acousticness, instrumentalness, valence, and tempo have decreased or stayed constant over time.

- Genres with high Danceability also tend to have high Energy and Loudness.

- All genres have low Speechiness, Acousticness, Instrumentalness, and Liveness.

- R&B, Hip-Hop, and Latin all have similar audio features.

- Country, Rock, and Indie have similar features.

- Pop and EDM have similar features.

Shooting Percentage in Close Home Games vs Close Away Games
=============================================================


Inputs {.sidebar}
-------------------------
```{r, echo=FALSE}

inputPanel(
 selectInput("teams6", label = "Home Team Graph:", 
             choices = c("Atlanta Dream" = "Atlanta Dream",
                         "Chicago Sky" = "Chicago Sky",
                         "Connecticut Sun" = "Connecticut Sun",
                         "Dallas Wings" = "Dallas Wings",
                         "Indiana Fever" = "Indiana Fever",
                         "Las Vegas Aces" = "Las Vegas Aces",
                         "Los Angeles Spark" = "Los Angeles Spark",
                         "Minnesota Lynx" = "Minnesota Lynx",
                         "Phoenix Mercury" = "Phoenix Mercury",
                         "Seattle Storm" = "Seattle Storm",
                         "Washington Mystics" = "Washington Mystics",
                         "New York Liberty" = "New York Liberty"))
)
```

Row
-------------------------------------

```{r}
renderPlot({
ggplot(all_shots_made, aes(x = team, y = n, fill = made_shot))  +
  geom_bar(color = "black", stat = "identity") +
  scale_fill_manual(values = c("white", "#E77500")) +
    theme(panel.background = element_rect(fill = "gray80"), panel.grid.minor = element_blank(),
          plot.title = element_text(hjust = 0.5, face = "bold", size = 19),
          legend.title = element_text(face = "bold")) +
  labs(title = "Number of Shots Made vs. Missed in Close Games",
       x = "WNBA Team",
       y = "Number of Shots",
       fill = "Made or Missed"
       )

 }, height = 500, width = 605)

```


```{r, echo=FALSE}

renderPlot({
all_close_game_shots |> 
    filter(shooting_team == input$teams6) |>
ggplot(aes(x = shooting_team, fill = made_shot))  +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("white", "#E77500")) +
    theme(panel.background = element_rect(fill = "gray80"), 
          panel.grid.minor = element_blank(),
          legend.title = element_text(face = "bold")) +
  labs(title = "Number of Shots Made vs. Missed in Close Games",
       x = "WNBA Team",
       y = "Number of Shots",
       fill = "Made or Missed"
       )

 }, height = 500, width = 605)

 
```


Row
-------------------------------------

```{r}

renderPlot({
ggplot(all_close_game_shots, aes(x = Shooting_Team_Home_Away)) +
  geom_bar(aes(fill = made_shot), color = "black", position = "fill") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("white", "#E77500")) +
  labs(title = "Shooting Percentage For Home And Away Teams In Close Games",
       x = "Home vs. Away",
       fill = "Result") +
  theme(panel.background = element_rect(fill = "gray80"), 
        panel.grid.minor = element_blank(),
        legend.title = element_text(face = "bold"))
 }, height = 500, width = 605)


```


```{r}
renderPlot({
all_close_game_shots |> 
    filter(shooting_team == input$teams6) |>
    ggplot(aes(x = Shooting_Team_Home_Away)) +
    geom_bar(aes(fill = made_shot), color = "black", position = "fill") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    scale_fill_manual(values = c("white", "#E77500")) +
    labs(title = "Each Team's Shotting Percentage For Home vs. Away Close Games",
       x = "Home vs. Away",
       fill = "Result") +
  theme(panel.background = element_rect(fill = "gray80"), 
        panel.grid.minor = element_blank(),
        legend.title = element_text(face = "bold")) 
 }, , height = 500, width = 605)

```

Row
-------------------------------------


```{r}

renderPlot({
  ggplot(all_close_game_shots, aes(x = Shooting_Team_Home_Away, fill = Shooting_Team_Home_Away), height = 500, width = 605)  +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("#161616", "#B54213")) +
    theme(panel.background = element_rect(fill = "gray80"), 
          panel.grid.minor = element_blank(),
          legend.title = element_text(face = "bold")) +
  labs(title = "Number of Shots Home vs. Away in Close Games",
       x = "WNBA Team",
       y = "Number of Shots",
       fill = "Home Or Away") 

}, height = 500, width = 605)  # Set the dimensions here



```

```{r, echo=FALSE}

renderPlot({
all_close_game_shots |> 
    filter(shooting_team == input$teams6) |>
ggplot(aes(x = Shooting_Team_Home_Away, fill = Shooting_Team_Home_Away))  +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("#161616", "#B54213")) +
    theme(panel.background = element_rect(fill = "gray80"), 
          panel.grid.minor = element_blank(),
          legend.title = element_text(face = "bold")) +
  labs(title = "Number of Shots Home vs. Away in Close Games",
       x = "WNBA Team",
       y = "Number of Shots",
       fill = "Home Or Away"
       )

 }, height = 500, width = 605)

 
```


Row
-------------------------

### **Question & Plots Explanation:**

**Question 1:** The first question we chose to look at is how the various audio features differ by genre. 



**Plots Explanation:** The left plot analyzes these features over time and the right plot measures the frequency of each feature by genre. The viewer has the ability to compare different genres and observe how the audio features have changed over time or compare the frequency of various audio features.


### **Observations / Conclusions:**

- For the majority of genres, danceability, loudness, and liveness have increased over time.

- For the majority of genres, energy, speechiness, acousticness, instrumentalness, valence, and tempo have decreased or stayed constant over time.

- Genres with high Danceability also tend to have high Energy and Loudness.

- All genres have low Speechiness, Acousticness, Instrumentalness, and Liveness.

- R&B, Hip-Hop, and Latin all have similar audio features.

- Country, Rock, and Indie have similar features.

- Pop and EDM have similar features.


Comparing Teams To Each Other
=============================================================

Inputs {.sidebar}
-------------------------

```{r, echo=FALSE}

 inputPanel(
    checkboxGroupInput("teams_check8", "Select Teams For Wins vs Losses:",
                       choices = c("All", unique(as.character(win_losses2$teams))),                         
                       selected = "All")
  )
```

```{r, echo=FALSE}

 inputPanel(
    checkboxGroupInput("teams_check7", "Select Teams For Shooting Percentage:",
                       choices = c("All", unique(as.character(all_close_game_shots$shooting_team))),                         
                       selected = "All")
  )
```

Row
-------------------------------------
```{r, echo=FALSE}


renderPlot({
    filtered_teams1 <- if("All" %in% input$teams_check8) {
      win_loss_per_team
    } else {
      win_loss_per_team |>
        filter(team %in% input$teams_check8)
    }

  ggplot(filtered_teams1, aes(x = home_or_away, y = occurences, fill = result)) +
  geom_bar(position = position_fill(), stat = "identity") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("firebrick", "goldenrod1", "green4")) +
  labs(title = "Outcomes For Home And Away Teams In Close Games",
       x = "Home vs. Away",
       fill = "Result") +
  facet_wrap(~team)+
    theme(strip.text = element_text(
    size = 20))
 }, height = 600, width = 1210)
```

Row
-------------------------------------

```{r, echo=FALSE}
renderPlot({
    filtered_teams7 <- if("All" %in% input$teams_check7) {
      all_close_game_shots
    } else {
      all_close_game_shots |>
        filter(shooting_team %in% input$teams_check7)
    }

ggplot(filtered_teams7, aes(x = Shooting_Team_Home_Away)) +
  geom_bar(aes(fill = made_shot), color = "black", position = "fill") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("white", "#E77500")) +
  labs(title = "Each Team's Shotting Percentage For Home vs. Away Close Games",
       x = "Home vs. Away",
       fill = "Result") +
  theme_gray() +
  facet_wrap(~shooting_team) +
  theme(strip.text = element_text(
    size = 20))
 }, height = 600, width = 1210)

 
```


Row
-------------------------

### **Question & Plots Explanation:**

**Question 1:** The first question we chose to look at is how the various audio features differ by genre. 



**Plots Explanation:** The left plot analyzes these features over time and the right plot measures the frequency of each feature by genre. The viewer has the ability to compare different genres and observe how the audio features have changed over time or compare the frequency of various audio features.


### **Observations / Conclusions:**

- For the majority of genres, danceability, loudness, and liveness have increased over time.

- For the majority of genres, energy, speechiness, acousticness, instrumentalness, valence, and tempo have decreased or stayed constant over time.

- Genres with high Danceability also tend to have high Energy and Loudness.

- All genres have low Speechiness, Acousticness, Instrumentalness, and Liveness.

- R&B, Hip-Hop, and Latin all have similar audio features.

- Country, Rock, and Indie have similar features.

- Pop and EDM have similar features.


WNBA Team Shooting
==========================

Inputs {.sidebar}
-------------------------

```{r, echo=FALSE}
inputPanel(
 selectInput("teams",
                        "Select a Team",
                        choices = c("Atlanta Dream", "Chicago Sky",
                                    "Connecticut Sun", "Dallas Wings", 
                                    "Indiana Fever", "Las Vegas Aces",
                                    "Los Angeles Spark", "Minnesota Lynx",
                                    "New York Liberty", "Phoenix Mercury",
                                    "Seattle Storm", "Washington Mystics"))
)

```

Row 
-------------------------

```{r, echo = FALSE}
renderPlot({
  # create data
  team_data <- wnba_shot_chart |>
    filter(shooting_team == input$teams)
  
  # plot
  nyl_court +
    stat_summary_hex(
      data = team_data,
      aes(
        x = coordinate_y,
        y = coordinate_x,
        z = made_shot,
        group = -1
      ),
      binwidth = c(2, 2),
      fun = mean,
      color = "black",
      alpha = .8
    ) +
    scale_fill_gradient(low = "white", high = "darkorange3") +
    labs(fill = "Shooting Rate",
         title = paste(input$teams, "Shooting Efficiency")) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold", size = 28),
      legend.title.position = "top",
      legend.title = element_text(size = 16, face = "bold", hjust = 0.5),
      legend.key.size = unit(0.5, "inches"),
      legend.text = element_text(size = 12)
    )
}, height = 500, width = 605)
```

```{r, echo=FALSE}
renderPlot({
  # create data
  team_data <- wnba_shot_chart |>
    filter(shooting_team == input$teams)
  
  # plot
  nyl_court +
    geom_hex(
      data = team_data,
      aes(x = coordinate_y, y = coordinate_x),
      binwidth = c(2, 2),
      alpha = 0.8,
      color = "black"
    ) +
    scale_fill_gradient(low = "white", high = "darkorange3") +
    labs(fill = "# of Shots",
         title = paste(input$teams, "Shooting Frequency")) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold", size = 28),
      legend.title.position = "top",
      legend.title = element_text(size = 16, face = "bold", hjust = 0.5),
      legend.key.size = unit(0.5, "inches"),
      legend.text = element_text(size = 12)
    )
}, height = 500, width = 605)
```


Row
-------------------------

### **Question & Plots Explanation:**

**Question 1:** The first question we chose to look at is how the various audio features differ by genre. 



**Plots Explanation:** The left plot analyzes these features over time and the right plot measures the frequency of each feature by genre. The viewer has the ability to compare different genres and observe how the audio features have changed over time or compare the frequency of various audio features.


### **Observations / Conclusions:**

- For the majority of genres, danceability, loudness, and liveness have increased over time.

- For the majority of genres, energy, speechiness, acousticness, instrumentalness, valence, and tempo have decreased or stayed constant over time.

- Genres with high Danceability also tend to have high Energy and Loudness.

- All genres have low Speechiness, Acousticness, Instrumentalness, and Liveness.

- R&B, Hip-Hop, and Latin all have similar audio features.

- Country, Rock, and Indie have similar features.

- Pop and EDM have similar features.

Player Shooting
==========================

Inputs {.sidebar}
-------------------------

```{r, echo=FALSE}
inputPanel(
 selectInput("teams",
                        "Select a Team",
                        choices = c("Atlanta Dream", "Chicago Sky",
                                    "Connecticut Sun", "Dallas Wings", 
                                    "Indiana Fever", "Las Vegas Aces",
                                    "Los Angeles Spark", "Minnesota Lynx",
                                    "New York Liberty", "Phoenix Mercury",
                                    "Seattle Storm", "Washington Mystics"))
)

renderUI({
           selectInput("players",
                        "Select a Player",
                        choices = wnba_shot_chart |> 
                filter(shooting_team == as.character(input$teams)) |> 
                  distinct(shooting_player) |> 
                  arrange(shooting_player))
        })


```


Row 
-------------------------


```{r, echo = FALSE}
renderPlot({
  # create data
  player_data <- wnba_shot_chart |> 
  filter(shooting_player == input$players & shooting_team == input$teams)
  
  # plot
  nyl_court +
    stat_summary_hex(
      data = player_data,
      aes(
        y = coordinate_x,
        x = coordinate_y,
        z = made_shot,
        group = -1
      ),
      binwidth = c(2, 2),
      fun = mean,
      color = "black",
      alpha = .8
    ) +
    scale_fill_gradient(low = "white", high = "darkorange3") +
    labs(fill = "Shooting Rate", title = paste(input$players, "Shooting Efficiency")) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold", size = 28),
      legend.title.position = "top",
      legend.title = element_text(size = 16, face = "bold", hjust = 0.5),
      legend.key.size = unit(0.5, "inches"),
      legend.text = element_text(size = 12)
    )
}, height = 500, width = 605)
```

```{r, echo=FALSE}
renderPlot({
  # create data
  player_data <- wnba_shot_chart |> 
  filter(shooting_player == input$players & shooting_team == input$teams)
  
  # plot
  nyl_court +
    geom_hex(
      data = player_data,
      aes(y = coordinate_x, x = coordinate_y),
      binwidth = c(2, 2),
      color = "black",
      alpha = 0.8
    ) +
    scale_fill_gradient(low = "white", high = "darkorange3") +
    labs(fill = "# of Shots", title = paste(input$players, "Shooting Frequency")) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold", size = 28),
      legend.title.position = "top",
      legend.title = element_text(size = 16, face = "bold", hjust = 0.5),
      legend.key.size = unit(0.5, "inches"),
      legend.text = element_text(size = 12)
    )
}, height = 500, width = 605)
```


Row
-------------------------

### **Question & Plots Explanation:**

**Question 1:** The first question we chose to look at is how the various audio features differ by genre. 



**Plots Explanation:** The left plot analyzes these features over time and the right plot measures the frequency of each feature by genre. The viewer has the ability to compare different genres and observe how the audio features have changed over time or compare the frequency of various audio features.


### **Observations / Conclusions:**

- For the majority of genres, danceability, loudness, and liveness have increased over time.

- For the majority of genres, energy, speechiness, acousticness, instrumentalness, valence, and tempo have decreased or stayed constant over time.

- Genres with high Danceability also tend to have high Energy and Loudness.

- All genres have low Speechiness, Acousticness, Instrumentalness, and Liveness.

- R&B, Hip-Hop, and Latin all have similar audio features.

- Country, Rock, and Indie have similar features.

- Pop and EDM have similar features.