---
title: "WNBA Shooting"
author: "Liam Jennings"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: 
      version: 4
      bootswatch: flatly
runtime: shiny
---

# About

### **Additional Information:**

**Authors:**

Liam Jennings

**Objective:**

Although we outlined a few questions, our shiny app gives viewers the flexibility to look at many different questions regarding Spotify artists and their audio features. We hope that viewers may be able to learn more about their favorite genre and be able to find similarities and differences between their favorite and least favorite genres.

**Tribulations and Victories of Data Acquisition and Wrangling:**

After acquiring a Spotify ID and access token, we were able to view all Spotify data on an artist or song by using either it's name or it's unique ID. Originally, we had wanted to analyze at least five artists per genre in order to build a larger dataset and have more accurate analysis. However, our for loop was inconsistent with the large amount of data and had a difficult time finding the correct artists based of off their ID. Each time we ran the for loop, we would receive a dataset with a different number of artists. Due to this, we ended up reducing our sample size and looking at between three and five artists per genre. This was a significantly smaller number and allowed the for loop to work accurately, which enabled us to produce our final dataset.

**Color Scheme:**

Since our data was pulled from Spotify, we wanted our graphs to all have a color scheme related to Spotify. Unfortunately, for the graph on the Audio Features Part 2 page, too many colors were required for points that overlapped, making it impossible to find a solution where the colors were all different. As a result, we stuck with the scale_color_calc() color scale. On all the other graphs, we used shades of green, grey, and black (the Spotify colors) to represent the data. On the Audio Features Part 1 page we were able to use the same shade of green that is in the official Spotify logo.

### **Defining The Variables**

-   **Danceability:** How suitable a track is for dancing based on a combination of musical elements including tempo, rhythm stability, and beat strength.

-   **Energy:** A measure of intensity and activity that ranges from 0.0 to 1.0.

-   **Loudness:** The overall loudness of a track in decibels (dB).

-   **Speechiness:** Detects the presence of spoken words in a track. The values range from 0.0 to 1.0.

-   **Acousticness:** A measure of how acoustic a track is. Ranges from 0.0 to 1.0.

-   **Instrumentalness:** Measures the amount of vocal content in a track. Ranges from 0.0 to 1.0 with 1.0 being more instrumental.

-   **Liveness:** Detects the presence of an audience in the track, such as if the track was performed live or not. Ranges from 0.0 to 1.0.

-   **Valence:** Describes the musical positiveness of a track. The more positive a track is, the closer the value is to 1.0.

-   **Tempo:** The overall estimated tempo of a track in beats per minute (BPM).

-   **Key:** Represents the musical key of a track (A, A#, B, C, C#, D, D#, E, F, F#, G, and G#).

-   **Mode:** Indicates whether a track is in a major or minor key.

```{r global, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(flexdashboard)
#library(shinydashboard)
library(shiny)
library(bslib)
library(patchwork)
library(sportyR)
library(stringr)
theme_set(theme_bw())
wnba_shots <- read_csv("https://raw.githubusercontent.com/36-SURE/36-SURE.github.io/main/data/wnba_shots.csv")

#View(wnba_shots)
```


```{r, echo = FALSE}
# Removed The All Star Game & Added New Variables
wnba_shots <- wnba_shots |>
  filter(shooting_team != "Team Stewart" & shooting_team != "Team Wilson") |>  # Removes All Star Games
   mutate(shooting_player = ifelse(
      str_detect(desc, "blocks") == TRUE,
      sub(".*?\\b(?:blocks)\\W+(\\w+(?:\\W+\\w+){0,2})\\b(?:'s| 's| B. 's)\\s.*", "\\1", desc, perl = TRUE), sub("\\ makes.*|\\ misses.*|\\ B. makes.*|\\ B. misses.*", "\\1", desc)), # Finds who shot the ball
         score_differential = home_score - away_score, # Determines Score Differential After Shot
         free_throw = if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 3 of"), 3,
       if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 2 of"), 2,
               if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 1 of") | str_detect(shot_type, "[Tt]echnical"), 1, 0))), # Determines what freethrow it was 
       made_shot = if_else(made_shot == "TRUE", "Made", "Missed"),  
       Shooting_Team_Home_Away = if_else(shooting_team == home_team_name, "Home", "Away"),  #Determines if the shooting team was home or away
    coordinate_x = abs(coordinate_x),   
    # rename shooting_team to include team name
    shooting_team = case_match(
      shooting_team,
      "Atlanta" ~ "Atlanta Dream",
      "Chicago" ~ "Chicago Sky",
      "Connecticut" ~ "Connecticut Sun",
      "Dallas" ~ "Dallas Wings",
      "Indiana" ~ "Indiana Fever",
      "Las Vegas" ~ "Las Vegas Aces",
      "Los Angeles" ~ "Los Angeles Spark",
      "Minnesota" ~ "Minnesota Lynx",
      "New York" ~ "New York Liberty",
      "Phoenix" ~ "Phoenix Mercury",
      "Seattle" ~ "Seattle Storm",
      "Washington" ~ "Washington Mystics"
    ),
    home_team_name = case_match(
      home_team_name,
      "Atlanta" ~ "Atlanta Dream",
      "Chicago" ~ "Chicago Sky",
      "Connecticut" ~ "Connecticut Sun",
      "Dallas" ~ "Dallas Wings",
      "Indiana" ~ "Indiana Fever",
      "Las Vegas" ~ "Las Vegas Aces",
      "Los Angeles" ~ "Los Angeles Spark",
      "Minnesota" ~ "Minnesota Lynx",
      "New York" ~ "New York Liberty",
      "Phoenix" ~ "Phoenix Mercury",
      "Seattle" ~ "Seattle Storm",
      "Washington" ~ "Washington Mystics"),
    away_team_name = case_match(
      away_team_name,
      "Atlanta" ~ "Atlanta Dream",
      "Chicago" ~ "Chicago Sky",
      "Connecticut" ~ "Connecticut Sun",
      "Dallas" ~ "Dallas Wings",
      "Indiana" ~ "Indiana Fever",
      "Las Vegas" ~ "Las Vegas Aces",
      "Los Angeles" ~ "Los Angeles Spark",
      "Minnesota" ~ "Minnesota Lynx",
      "New York" ~ "New York Liberty",
      "Phoenix" ~ "Phoenix Mercury",
      "Seattle" ~ "Seattle Storm",
      "Washington" ~ "Washington Mystics"))

  
  

#View(wnba_shots)
```

```{r, echo = FALSE}
# Shots taken in the last 30 seconds of the fourth quarter Where the score differential was less than 6 after the shot was taken
end_of_game_shots <- wnba_shots |>
  filter(game_seconds_remaining <= 30 & score_differential %in% c(-6, -5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6) & qtr == 4) 

# All Close Games
all_close_games <- end_of_game_shots|> 
  distinct(game_id) 

# All Shots Taken In Last 30 Seconds 
all_shots <- wnba_shots|>
  filter(game_seconds_remaining <= 30 & qtr == 4) 
  
# All Shots Taken In Last 30 Seconds In Close Games
all_close_game_shots <- left_join(all_close_games, all_shots) |> 
  mutate(made_shot = factor(made_shot,levels = c("Missed", "Made"))) |> 
  arrange(shooting_team)

# The earliest time within the last 30 seconds where a shot occurred for a close game
close_games <- end_of_game_shots |> 
  group_by(game_id) |> 
  slice_max(game_seconds_remaining) |> 
  arrange(-free_throw) |> 
  slice_head() |> 
  select(game_id, home_team_name, away_team_name, score_differential) 


# The score after the last shot of every game 
final_score <- wnba_shots |> 
  group_by(game_id) |> 
  slice_min(game_seconds_remaining) |> 
  arrange(free_throw) |> 
  slice_head() |> 
   rename(final_score_differential = score_differential) |> 
   select(game_id, final_score_differential) 

# Score Change From First Shot In Last 30 Seconds To Last Shot of Game & Final Outcomes Added
close_games_observing <- left_join(close_games, final_score) |> 
  mutate(home_team_outcome =  
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential == final_score_differential, "Won - Kept Same Lead",
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential > final_score_differential, "Won - Lead Decreased",
 if_else(score_differential > 0 & final_score_differential > 0, "Won - Extended Lead",
 if_else(score_differential > 0 & final_score_differential == 0, "Tied - Lost Lead", 
 if_else(score_differential > 0 & final_score_differential < 0, "Lost - Lost Lead", 
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential == final_score_differential, "Lost - No Comeback",
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential > final_score_differential, "Lost - Deficit Increased",
 if_else(score_differential < 0 & final_score_differential < 0 & final_score_differential > score_differential, "Lost - Deficit Decreased",
 if_else(score_differential < 0 & final_score_differential == 0, "Tied - Comeback",
 if_else(score_differential == 0 & final_score_differential == 0, "Tied - No Change",
 if_else(score_differential == 0 & final_score_differential > 0, "Won - From Tie",
 if_else(score_differential == 0 & final_score_differential < 0, "Lost - From Tie", 
         "Won - Took Lead From Loss")))))))))))),
 away_team_outcome =  
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential == final_score_differential, "Lost - No Comeback",
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential > final_score_differential, "Lost - Deficit Decreased",
 if_else(score_differential > 0 & final_score_differential > 0, "Lost - Deficit Increased",
 if_else(score_differential > 0 & final_score_differential == 0, "Tied - Comeback", 
 if_else(score_differential > 0 & final_score_differential < 0, "Won - Took Lead From Loss", 
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential == final_score_differential, "Won - Kept Same Lead",
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential > final_score_differential, "Won - Extended Lead",
 if_else(score_differential < 0 & final_score_differential < 0 & final_score_differential > score_differential, "Won - Lead Decreased",
 if_else(score_differential < 0 & final_score_differential == 0, "Tied - Lost Lead",
 if_else(score_differential == 0 & final_score_differential == 0, "Tied - No Change",
 if_else(score_differential == 0 & final_score_differential > 0, "Lost - From Tie",
 if_else(score_differential == 0 & final_score_differential < 0, "Won - From Tie", 
         "Lost - Lost Lead")))))))))))),
 Home_Result = if_else(str_detect(home_team_outcome, "^Won"), "Win",
                       if_else(str_detect(home_team_outcome, "^Lost"), "Loss", "Tie")),
         Away_Result = if_else(str_detect(away_team_outcome, "^Won"), "Win",
                       if_else(str_detect(away_team_outcome, "^Lost"), "Loss", "Tie")))|> 
  ungroup() |> 
  mutate(away_team_outcome = factor(away_team_outcome, levels = c("Lost - Lost Lead", "Lost - Deficit Increased", "Lost - No Comeback", "Lost - Deficit Decreased", "Lost - From Tie", "Tied - Lost Lead", "Tied - No Change", "Tied - Comeback", "Won - Lead Decreased", "Won - Kept Same Lead", "Won - Extended Lead", "Won - From Tie", "Won - Took Lead From Loss")),
         home_team_outcome =factor(home_team_outcome, levels = c("Lost - Lost Lead", "Lost - Deficit Increased", "Lost - No Comeback", "Lost - Deficit Decreased", "Lost - From Tie", "Tied - Lost Lead", "Tied - No Change", "Tied - Comeback", "Won - Lead Decreased", "Won - Kept Same Lead", "Won - Extended Lead", "Won - From Tie", "Won - Took Lead From Loss")))


win_loss_type_color_vector <- c("Lost - Lost Lead" = "firebrick4", "Lost - Deficit Increased" = "firebrick", "Lost - No Comeback" = "firebrick3", "Lost - Deficit Decreased" = "firebrick2", "Lost - From Tie" = "firebrick1", "Tied - Lost Lead" = "darkorange1", "Tied - No Change" = "goldenrod1", "Tied - Comeback" = "gold", "Won - Lead Decreased" = "lightgreen", "Won - Kept Same Lead" = "green1", "Won - Extended Lead" = "green3", "Won - From Tie" = "green4", "Won - Took Lead From Loss" = "darkgreen")


# Counts number of home close game wins and losses per team
home_win_loss <- close_games_observing |> 
  group_by(home_team_name, Home_Result) |> 
  summarise(num_times_home = n()) |> 
  rename(team = home_team_name,
         result = Home_Result)

# Counts number of away close game wins and losses per team
away_win_losses <- close_games_observing |> 
  group_by(away_team_name, Away_Result) |> 
  summarise(num_times_away = n()) |> 
  rename(team = away_team_name,
         result = Away_Result)

# Combines both Away And Home Wins and losses in close games 
win_loss_per_team <- full_join(away_win_losses, home_win_loss) |> 
 mutate(num_times_home = replace_na(num_times_home, 0),
        num_times_away = replace_na(num_times_away, 0)) |> 
  pivot_longer(num_times_home:num_times_away,
               values_to = "occurences",
               names_to = "home_or_away") |> 
  mutate(home_or_away = ifelse(home_or_away == "num_times_home", "Home", "Away"),
         result = factor(result, levels = c("Loss", "Tie", "Win"))) |> 
  ungroup() 

# win_loss_per_team


win_loss_color_vector <- c("firebrick", "goldenrod1", "green4")

names(win_loss_color_vector) <- levels(win_loss_per_team$result)

# Win, Tie, Loss Color Assignment 
custom_color <- scale_fill_manual(name = "Result", values = win_loss_color_vector)

# Both Away And Home Win vs. Loss In League
win_losses <- close_games_observing |>
  pivot_longer(Home_Result:Away_Result,
               values_to = "win_or_loss",
               names_to = "home_or_away_result") |> 
  mutate(home_or_away_result = ifelse(home_or_away_result == "Home_Result", "Home", "Away"))
         
#win_losses

# Determines if team was home or away 
win_losses2 <- close_games_observing |>
  pivot_longer(home_team_name:away_team_name,
               values_to = "teams",
               names_to = "home_or_away_team") |> 
  mutate(home_or_away_team = ifelse(home_or_away_team == "home_team_name", "Home", "Away")) |> 
  arrange(teams)


# Home Team Outcome Type By League
num_home_outcomes <- close_games_observing |>
  select(home_team_outcome, Home_Result) |> 
  count(home_team_outcome, Home_Result) |> 
  rename(num_times_home = n,
         outcome = home_team_outcome)

# Away Team Outcome By League
num_away_outcomes <- close_games_observing |>
  select(away_team_outcome, Away_Result) |> 
  count(away_team_outcome, Away_Result) |> 
  rename(num_times_away = n,
         outcome = away_team_outcome) 

#num_away_outcomes


# Number of Occurrences of All Outcome Types For Home vs. Away in league
possible_outcomes <- full_join(num_home_outcomes, num_away_outcomes, by = "outcome") |> 
  mutate(num_times_home = replace_na(num_times_home, 0),
         num_times_away = replace_na(num_times_away, 0),
         Win_Loss = ifelse(is.na(Away_Result), Home_Result, Away_Result)) |> 
  select(-Home_Result, -Away_Result)

#possible_outcomes

# Home Team Outcome Type By Team 
home_game_results <- close_games_observing |> 
  group_by(home_team_name, home_team_outcome, Home_Result) |>
  summarise(num_times_home_per_team = n()) |> 
  rename(outcome = home_team_outcome) |> 
  ungroup()
#home_game_results

# Away Game Outcome Type By Team
away_game_results <- close_games_observing |> 
  group_by(away_team_name, away_team_outcome, Away_Result) |> 
  summarise(times_occured_away_per_team = n()) |> 
  rename(outcome = away_team_outcome) |> 
  ungroup()

#away_game_results

# Number of shots made vs missed in league
all_shots_made <- all_close_game_shots |> 
  count(made_shot) 

all_shots_made$team <- c("Entire League", "Entire League")

#### Shot Cart Clean dataset
wnba_shot_chart <- wnba_shots |>
  # filter by regular season and remove outliers
  filter(game_type == 2 & abs(coordinate_x) >= 10 &
           # remove Free Throws 
           str_like(shot_type, "Free Throw%") == FALSE) 
  
# WNBA court (New York Libery)
nyl_court <- sportyR::geom_basketball("WNBA", display = "offense", rotation = 90,
                                      color_updates = list(
                                        panel_background = "black",
                                        offensive_half_court = "gray",
                                        court_apron = "#6ECEB2",
                                        center_circle_outline = "white",
                                        center_circle_fill = "#6ECEB2",
                                        endline = "white",
                                        sideline = "white",
                                        division_line = "white",
                                        two_point_range = "#857e82",
                                        painted_area = "#2a2729",
                                        lane_boundary = "white",
                                        free_throw_circle_fill = "#857e82",
                                        inbounding_line = "white",
                                        substitution_line = "white",
                                        three_point_line = "white",
                                        lane_space_mark = "white",
                                        free_throw_circle_outline = "#6ECEB2",
                                        free_throw_circle_dash = "#6ECEB2",
                                        baseline_lower_defensive_box = "white",
                                        lane_lower_defensive_box = "#6ECEB2",
                                        restricted_arc = "#6ECEB2"
                                      ))
```

# WNBA Team Shooting

## Row

```{r, echo=FALSE}
inputPanel(
 selectInput("teams",
                        "Select a Team",
                        choices = c("Atlanta Dream", "Chicago Sky",
                                    "Connecticut Sun", "Dallas Wings", 
                                    "Indiana Fever", "Las Vegas Aces",
                                    "Los Angeles Spark", "Minnesota Lynx",
                                    "New York Liberty", "Phoenix Mercury",
                                    "Seattle Storm", "Washington Mystics"))
)

```

## Row

```{r, echo = FALSE}
renderPlot({
  # create data
  team_data <- wnba_shot_chart |>
    filter(shooting_team == input$teams)
  
  # plot
  nyl_court +
    stat_summary_hex(
      data = team_data,
      aes(
        x = coordinate_y,
        y = coordinate_x,
        z = made_shot,
        group = -1
      ),
      binwidth = c(2, 2),
      fun = mean,
      color = "black",
      alpha = .8
    ) +
    scale_fill_gradient(low = "white", high = "darkorange3") +
    labs(fill = "Shooting Rate",
         title = paste(input$teams, "Shooting Efficiency")) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold", size = 20)
    )
})
```

```{r, echo=FALSE}
renderPlot({
  # create data
  team_data <- wnba_shot_chart |>
    filter(shooting_team == input$teams)
  
  # plot
  nyl_court +
    geom_hex(
      data = team_data,
      aes(x = coordinate_y, y = coordinate_x),
      binwidth = c(2, 2),
      alpha = 0.8,
      color = "black"
    ) +
    scale_fill_gradient(low = "white", high = "darkorange3") +
    labs(fill = "# of Shots",
         title = paste(input$teams, "Shooting Frequency")) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(
        hjust = 0.5,
        face = "bold",
        size = 20
      )
    )
})
```

## Row

### **Question & Plots Explanation:**

**Question 1:** The first question we chose to look at is how the various audio features differ by genre.

**Plots Explanation:** The left plot analyzes these features over time and the right plot measures the frequency of each feature by genre. The viewer has the ability to compare different genres and observe how the audio features have changed over time or compare the frequency of various audio features.

### **Observations / Conclusions:**

-   For the majority of genres, danceability, loudness, and liveness have increased over time.

-   For the majority of genres, energy, speechiness, acousticness, instrumentalness, valence, and tempo have decreased or stayed constant over time.

-   Genres with high Danceability also tend to have high Energy and Loudness.

-   All genres have low Speechiness, Acousticness, Instrumentalness, and Liveness.

-   R&B, Hip-Hop, and Latin all have similar audio features.

-   Country, Rock, and Indie have similar features.

-   Pop and EDM have similar features.

# Player Shooting

## Row

```{r, echo=FALSE}
inputPanel(
 selectInput("teams",
                        "Select a Team",
                        choices = c("Atlanta Dream", "Chicago Sky",
                                    "Connecticut Sun", "Dallas Wings", 
                                    "Indiana Fever", "Las Vegas Aces",
                                    "Los Angeles Spark", "Minnesota Lynx",
                                    "New York Liberty", "Phoenix Mercury",
                                    "Seattle Storm", "Washington Mystics"))
)


```

```{r}
renderUI({
           selectInput("players",
                        "Select a Player",
                        choices = wnba_shot_chart |> 
                filter(shooting_team == as.character(input$teams)) |> 
                  distinct(shooting_player) |> 
                  arrange(shooting_player))
        })
```

## Row

```{r, echo = FALSE}
renderPlot({
  # create data
  player_data <- wnba_shot_chart |> 
  filter(shooting_player == "Breanna Stewart" & shooting_team == "Liberty")
  
  # plot
  nyl_court +
    stat_summary_hex(
      data = player_data,
      aes(
        y = coordinate_x,
        x = coordinate_y,
        z = made_shot,
        group = -1
      ),
      binwidth = c(2, 2),
      fun = mean,
      color = "black",
      alpha = .8
    ) +
    scale_fill_gradient(low = "white", high = "darkorange3") +
    labs(fill = "Shooting Rate", title = paste(input$players, "Shooting Efficiency")) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold", size = 20)
    )
})
```

```{r, echo=FALSE}
renderPlot({
  # create data
  player_data <- wnba_shot_chart |> 
  filter(shooting_player == input$players & shooting_team == input$teams)
  
  # plot
  nyl_court +
    geom_hex(
      data = player_data,
      aes(y = coordinate_x, x = coordinate_y),
      binwidth = c(2, 2),
      color = "black",
      alpha = 0.8
    ) +
    scale_fill_gradient(low = "white", high = "darkorange3") +
    labs(fill = "# of Shots", title = paste(input$players, "Shooting Frequency")) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold", size = 20)
    )
})
```

## Row

### **Question & Plots Explanation:**

**Question 1:** The first question we chose to look at is how the various audio features differ by genre.

**Plots Explanation:** The left plot analyzes these features over time and the right plot measures the frequency of each feature by genre. The viewer has the ability to compare different genres and observe how the audio features have changed over time or compare the frequency of various audio features.

### **Observations / Conclusions:**

-   For the majority of genres, danceability, loudness, and liveness have increased over time.

-   For the majority of genres, energy, speechiness, acousticness, instrumentalness, valence, and tempo have decreased or stayed constant over time.

-   Genres with high Danceability also tend to have high Energy and Loudness.

-   All genres have low Speechiness, Acousticness, Instrumentalness, and Liveness.

-   R&B, Hip-Hop, and Latin all have similar audio features.

-   Country, Rock, and Indie have similar features.

-   Pop and EDM have similar features.

```{r}
 player_data <- wnba_shot_chart |> 
  filter(shooting_player == "Breanna Stewart" & shooting_team == "New York Liberty")

  
  # plot
  nyl_court +
    stat_summary_hex(
      data = player_data,
      aes(
        y = coordinate_x,
        x = coordinate_y,
        z = made_shot,
        group = -1
      ),
      binwidth = c(2, 2),
      fun = mean,
      color = "black",
      alpha = .8
    ) +
    scale_fill_gradient(low = "white", high = "darkorange3") +
    labs(fill = "Shooting Rate", title = paste("Shooting Efficiency")) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold", size = 20)
    )
```

