---
title: "WNBA Eda Project - Belle Schmidt"
output: html_document
date: "2024-06-06"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
theme_set(theme_bw())
wnba_shots <- read_csv("https://raw.githubusercontent.com/36-SURE/36-SURE.github.io/main/data/wnba_shots.csv")

#View(wnba_shots)
```


```{r, include=FALSE}
# Removed The All Star Game & Added New Variables
wnba_shots <- wnba_shots |>
  filter(shooting_team != "Team Stewart" & shooting_team != "Team Wilson") |> 
   mutate(shooting_player = ifelse(
      str_detect(desc, "blocks") == TRUE,
      sub(".*?\\b(?:blocks)\\W+(\\w+(?:\\W+\\w+){0,2})\\b(?:'s| 's| B. 's)\\s.*", "\\1", desc, perl = TRUE), sub("\\ makes.*|\\ misses.*|\\ B. makes.*|\\ B. misses.*", "\\1", desc)),
         score_differential = home_score - away_score, 
         free_throw = if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 3 of"), 3,
       if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 2 of"), 2,
               if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 1 of") | str_detect(shot_type, "[Tt]echnical"), 1, 0))),
       made_shot = if_else(made_shot == "TRUE", "Made", "Missed"),
       Shooting_Team_Home_Away = if_else(shooting_team == home_team_name, "Home", "Away"))
  
  

#View(wnba_shots)
```

```{r, include=FALSE}
# Shots taken in the last 30 seconds of the fourth quarter Where the score differential was less than 6 after the shot was taken
end_of_game_shots <- wnba_shots |>
  filter(game_seconds_remaining <= 30 & score_differential %in% c(-6, -5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6) & qtr == 4) 

# All Close Games
all_close_games <- end_of_game_shots|> 
  distinct(game_id) 

# All Shots Taken In Last 30 Seconds 
all_shots <- wnba_shots|>
  filter(game_seconds_remaining <= 30 & qtr == 4) 
  
# All Shots Taken In Last 30 Seconds In Close Games
all_close_game_shots <- left_join(all_close_games, all_shots) |> 
  mutate(made_shot = factor(made_shot,levels = c("Missed", "Made"))) 


# The earliest time within the last 30 seconds where a shot occurred for a close game
close_games <- end_of_game_shots |> 
  group_by(game_id) |> 
  slice_max(game_seconds_remaining) |> 
  arrange(-free_throw) |> 
  slice_head() |> 
  select(game_id, home_team_name, away_team_name, score_differential) 


# The score after the last shot of every game 
final_score <- wnba_shots |> 
  group_by(game_id) |> 
  slice_min(game_seconds_remaining) |> 
  arrange(free_throw) |> 
  slice_head() |> 
   rename(final_score_differential = score_differential) |> 
   select(game_id, final_score_differential) 

# Score Change From First Shot In Last 30 Seconds To Last Shot of Game & Final Outcomes Added
close_games_observing <- left_join(close_games, final_score) |> 
  mutate(home_team_outcome =  
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential == final_score_differential, "Won - Kept Same Lead",
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential > final_score_differential, "Won - Lead Decreased",
 if_else(score_differential > 0 & final_score_differential > 0, "Won - Extended Lead",
 if_else(score_differential > 0 & final_score_differential == 0, "Tied - Lost Lead", 
 if_else(score_differential > 0 & final_score_differential < 0, "Lost - Lost Lead", 
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential == final_score_differential, "Lost - No Comeback",
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential > final_score_differential, "Lost - Deficit Increased",
 if_else(score_differential < 0 & final_score_differential < 0 & final_score_differential > score_differential, "Lost - Deficit Decreased",
 if_else(score_differential < 0 & final_score_differential == 0, "Tied - Comeback",
 if_else(score_differential == 0 & final_score_differential == 0, "Tied - No Change",
 if_else(score_differential == 0 & final_score_differential > 0, "Won - From Tie",
 if_else(score_differential == 0 & final_score_differential < 0, "Lost - From Tie", 
         "Won - Took Lead From Loss")))))))))))),
 away_team_outcome =  
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential == final_score_differential, "Lost - No Comeback",
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential > final_score_differential, "Lost - Deficit Decreased",
 if_else(score_differential > 0 & final_score_differential > 0, "Lost - Deficit Increased",
 if_else(score_differential > 0 & final_score_differential == 0, "Tied - Comeback", 
 if_else(score_differential > 0 & final_score_differential < 0, "Won - Took Lead From Loss", 
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential == final_score_differential, "Won - Kept Same Lead",
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential > final_score_differential, "Won - Extended Lead",
 if_else(score_differential < 0 & final_score_differential < 0 & final_score_differential > score_differential, "Won - Lead Decreased",
 if_else(score_differential < 0 & final_score_differential == 0, "Tied - Lost Lead",
 if_else(score_differential == 0 & final_score_differential == 0, "Tied - No Change",
 if_else(score_differential == 0 & final_score_differential > 0, "Lost - From Tie",
 if_else(score_differential == 0 & final_score_differential < 0, "Won - From Tie", 
         "Lost - Lost Lead")))))))))))),
 Home_Result = if_else(str_detect(home_team_outcome, "^Won"), "Win",
                       if_else(str_detect(home_team_outcome, "^Lost"), "Loss", "Tie")),
         Away_Result = if_else(str_detect(away_team_outcome, "^Won"), "Win",
                       if_else(str_detect(away_team_outcome, "^Lost"), "Loss", "Tie")))|> 
  ungroup() |> 
  mutate(away_team_outcome = factor(away_team_outcome, levels = c("Lost - Lost Lead", "Lost - Deficit Increased", "Lost - No Comeback", "Lost - Deficit Decreased", "Lost - From Tie", "Tied - Lost Lead", "Tied - No Change", "Tied - Comeback", "Won - Lead Decreased", "Won - Kept Same Lead", "Won - Extended Lead", "Won - From Tie", "Won - Took Lead From Loss")),
         home_team_outcome =factor(home_team_outcome, levels = c("Lost - Lost Lead", "Lost - Deficit Increased", "Lost - No Comeback", "Lost - Deficit Decreased", "Lost - From Tie", "Tied - Lost Lead", "Tied - No Change", "Tied - Comeback", "Won - Lead Decreased", "Won - Kept Same Lead", "Won - Extended Lead", "Won - From Tie", "Won - Took Lead From Loss")))


win_loss_color_vector <- c("Lost - Lost Lead" = "firebrick4", "Lost - Deficit Increased" = "firebrick", "Lost - No Comeback" = "firebrick3", "Lost - Deficit Decreased" = "firebrick2", "Lost - From Tie" = "firebrick1", "Tied - Lost Lead" = "darkorange1", "Tied - No Change" = "goldenrod1", "Tied - Comeback" = "gold", "Won - Lead Decreased" = "lightgreen", "Won - Kept Same Lead" = "green1", "Won - Extended Lead" = "green3", "Won - From Tie" = "green4", "Won - Took Lead From Loss" = "darkgreen")

```

# Overarching Question 1 - How Does The League Overall Perform in Close Home Compared To Close Away Games?

## Close Game Wins vs. Losses Across Whole WNBA

```{r, include=FALSE}
# Both Away And Home Win vs. Loss In League
win_losses <- close_games_observing |>
  pivot_longer(Home_Result:Away_Result,
               values_to = "win_or_loss",
               names_to = "home_or_away_result") |> 
  mutate(home_or_away_result = ifelse(home_or_away_result == "Home_Result", "Home", "Away"))
         
win_losses
```

```{r}
# Home vs. Away Outcomes 
league_win_vs_losses <- ggplot(win_losses, aes(x = home_or_away_result, fill = win_or_loss)) +
  geom_bar(position = position_fill()) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("firebrick", "goldenrod1", "green4")) +
  labs(title = "Outcomes For Home And Away Teams In Close Games",
       x = "Home vs. Away",
       fill = "Result") 


league_win_vs_losses
```

Plot Description: From this plot we can determine that in a close WNBA game,
the away team is more likely to win than the home team.

## Outcome Type Related To Home and Away Across The League

```{r, include=FALSE}

# Home Team Results By League
num_home_outcomes <- close_games_observing |>
  select(home_team_outcome, Home_Result) |> 
  count(home_team_outcome, Home_Result) |> 
  rename(num_times_home = n,
         outcome = home_team_outcome)

# Away Team Results By League
num_away_outcomes <- close_games_observing |>
  select(away_team_outcome, Away_Result) |> 
  count(away_team_outcome, Away_Result) |> 
  rename(num_times_away = n,
         outcome = away_team_outcome) 

#num_away_outcomes


# Number of Occurences of All Outcomes For Home vs. Away
possible_outcomes <- full_join(num_home_outcomes, num_away_outcomes, by = "outcome") |> 
  mutate(num_times_home = replace_na(num_times_home, 0),
         num_times_away = replace_na(num_times_away, 0),
         Win_Loss = ifelse(is.na(Away_Result), Home_Result, Away_Result)) |> 
  select(-Home_Result, -Away_Result)

#possible_outcomes
```

```{r}
# Home Outcome Types Occured Across Leagues In Close Games

home_outcomes <- ggplot(possible_outcomes, aes(x = Win_Loss, y = num_times_home, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Occurences of Each Outcome Type For Home Teams",
       y = "Occurences",
       fill = "Outcome") +
  scale_fill_manual(values = win_loss_color_vector) +
  theme(axis.title.x = element_blank()) 



# Away Outcome Types Occured Across Leagues In Close Games
away_outcomes <- ggplot(possible_outcomes, aes(x = Win_Loss, y = num_times_away, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Occurences of Each Outcome Type For Away Teams",
       y = "Occurences",
       fill = "Outcome") +
  scale_fill_manual(values = win_loss_color_vector)+
  theme(axis.title.x = element_blank()) 

# Combined Graph of Away vs Home Team Outcomes; Point Out Away Teams Win More In Close Games
library(patchwork)

away_outcomes + home_outcomes +
  plot_layout(guides = "collect", nrow = 2) +
  labs("Occurences Of Each Outcome Type For Both Home and Away Teams In Close Games")
```

**Plot Description:** From the *Occurrences Of Each Outcome Type For
Both Home and Away Teams* graph, we can learn that in close games, the
team that won (regardless of if they were home or away) most likely
extended their lead between the time of the first shot in the last 30
seconds and the end of the game. This corresponds with the idea that the
team that lost, most likely lost with a higher deficit than what they
were down after the first shot in the last 30 seconds of the game. For
games that ended the 4th quarter with a tie, however, it is most likely
that a team had the lead after the first shot in the last 30 seconds but
then the other team tied it up. There were slightly more occurrences of
the away team having the lead and losing it, however, it is hard to
predict if home or away is a predictor because there were only a handful
of occurrences.

## League Shooting Percentage Home vs. Away

```{r}
  ggplot(all_close_game_shots, aes(x = Shooting_Team_Home_Away)) +
  geom_bar(aes(fill = made_shot), color = "black", position = "fill") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("white", "#E77500")) +
  labs(title = "Shooting Percentage For Home And Away Teams In Close Games",
       x = "Home vs. Away",
       fill = "Result") +
  theme_gray()
```

# Overarching Question 2 - How Do Each Of The Teams Perform In Close Home Compared To Close Away Games?

## Number of Close Home And Away Games (6 points or less with 30 seconds left) Per Team - Need ShinyApp 

```{r}
win_losses2 <- close_games_observing |>
  pivot_longer(home_team_name:away_team_name,
               values_to = "teams",
               names_to = "home_or_away_team") |> 
  mutate(home_or_away_team = ifelse(home_or_away_team == "home_team_name", "Home", "Away"))

win_losses2 |> 
  filter(teams == "Atlanta Dream")|> 
ggplot(aes(x = fct_rev(fct_infreq(teams)), fill = home_or_away_team)) +
  geom_bar(color = "black") +
  coord_flip() + 
  scale_fill_manual(values = c("white", "#E77500")) +
  labs(title = "Number of Close Home And Away Games Per Team", 
       y = "Number of Close Games",
       x = "WNBA Team",
       subtitle = "Close games is defined as a score differential of 6 or less in the last 30 seconds",
       fill = "Home or Away") +
  theme_gray()
```

## Each Team's Number of Wins And Losses In Close Home vs. Away Games - Need To Use Same Shiny App As Above

```{r, include=FALSE}
# Adds Both Away And Home Win vs. losses

home_win_loss <- close_games_observing |> 
  group_by(home_team_name, Home_Result) |> 
  summarise(num_times_home = n()) |> 
  rename(team = home_team_name,
         result = Home_Result)


away_win_losses <- close_games_observing |> 
  group_by(away_team_name, Away_Result) |> 
  summarise(num_times_away = n()) |> 
  rename(team = away_team_name,
         result = Away_Result)

         
win_loss_per_team <- full_join(away_win_losses, home_win_loss) |> 
 mutate(num_times_home = replace_na(num_times_home, 0),
        num_times_away = replace_na(num_times_away, 0)) |> 
  pivot_longer(num_times_home:num_times_away,
               values_to = "occurences",
               names_to = "home_or_away") |> 
  mutate(home_or_away = ifelse(home_or_away == "num_times_home", "Home", "Away")) |> 
  ungroup()

#win_loss_per_team
```

```{r}
# Home vs. Away Outcomes
team_win_vs_losses <- win_loss_per_team |> 
  ggplot(aes(x = home_or_away, y = occurences, fill = result)) +
  geom_bar(position = position_fill(), stat = "identity") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("firebrick", "goldenrod1", "green4")) +
  labs(title = "Outcomes For Home And Away Teams In Close Games",
       x = "Home vs. Away",
       fill = "Result") +
  facet_wrap(~team)


team_win_vs_losses
```

## Outcome Types For Each Team When Home vs. Away

```{r, include=FALSE}

# Home Team Results By Team 
home_game_results <- close_games_observing |> 
  group_by(home_team_name, home_team_outcome, Home_Result) |>
  summarise(num_times_home_per_team = n()) |> 
  rename(outcome = home_team_outcome) |> 
  ungroup()
home_game_results

# Away Game Results By Team
away_game_results <- close_games_observing |> 
  group_by(away_team_name, away_team_outcome, Away_Result) |> 
  summarise(times_occured_away_per_team = n()) |> 
  rename(outcome = away_team_outcome) |> 
  ungroup()

away_game_results
```

```{r}
# Home Outcome Types Occurred Across Leagues In Close Games - Need Shiny App
Team_home_outcomes <- home_game_results |>
  ungroup() |> 
  filter(home_team_name == "Atlanta")|> 
  ggplot(aes(x = Home_Result, y = num_times_home_per_team, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Occurences of Each Outcome When The Home Team",
       y = "Occurences",
       fill = "Outcome") +
  scale_fill_manual(values = win_loss_color_vector) +
  theme(axis.title.x = element_blank()) 

# Team_home_outcomes


# Away Outcome Types Occurred Across Leagues In Close Games - Need Shiny App

Team_away_outcomes <- away_game_results |>
  ungroup() |> 
  filter(away_team_name == "Atlanta")|> 
  ggplot(aes(x = Away_Result, y = times_occured_away_per_team, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Occurences of Each Outcome Type When The Away Team",
       y = "Occurences",
       fill = "Outcome") +
  scale_fill_manual(values = win_loss_color_vector) +
  theme(axis.title.x = element_blank()) 

# Combined Outcomes For Teams When They Are Home And Away

library(patchwork)

Team_home_outcomes + Team_away_outcomes +
  plot_layout(guides = "collect", nrow = 2) 
```

## Graph For Number of Shots Taken By Each of The WNBA Teams In Final 30 Seconds of Close Games - The Filter is to be changed by shiny app

```{r}
all_close_game_shots |> 
  filter(shooting_team == "Atlanta" | shooting_team == "Washington") |> 
  ggplot(aes(x = fct_rev(fct_infreq(shooting_team)), fill = made_shot))  +
  geom_bar(color = "black") +
  theme(axis.text.x=element_text(angle=45, hjust=0.9)) +
  scale_fill_manual(values = c("white", "#E77500")) +
  coord_flip() +
  labs(title = "Number of Shots Made vs. Missed in Close Games Per WNBA Team",
       x = "WNBA Team",
       y = "Number of Shots",
       fill = "Made or Missed"
       )
  
```


## Each Team's Shooting Percentage (Home and Away) - The Filter Is Changed By Same Shiny App As Above

```{r}
all_close_game_shots |> 
ggplot(aes(x = Shooting_Team_Home_Away)) +
  geom_bar(aes(fill = made_shot), color = "black", position = "fill") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("white", "#E77500")) +
  labs(title = "Each Team's Shotting Percentage For Home vs. Away Close Games",
       x = "Home vs. Away",
       fill = "Result") +
  theme_gray() +
  facet_wrap(~shooting_team)
```

# Overarching Question - How does time left in the game impact each team's performance?

- Make Graph For Shooting Percentage in the last 30 seconds per team
- Make Graph For Overall Shooting Percentage per team
- Make Graph For Final Possession Shooting Percentage per team
- Make Graph For Each Quarter's shooting percentage per team
- Make Graph For Start and end of half shooting percentage per team



```{r, include=FALSE}
# Shooting in the last 2 minutes of the Second Quarter
wnba_shots |>
  filter(qtr == 2 & quarter_seconds_remaining <= 120.0) |>
  arrange(quarter_seconds_remaining)

# Shooting in the last 2 minutes of the Fourth Quarter
wnba_shots |>
  filter(qtr == 4 & quarter_seconds_remaining <= 120.0) |>
  arrange(quarter_seconds_remaining)
```


## Teams Who Shot Best In Close Games (30 Seconds)

```{r, include=FALSE}
shots_made_data1 <- end_of_game_shots |>
   mutate(made_shot = if_else(made_shot == "TRUE", "Made", "Missed")) 



 shots_made_data <- end_of_game_shots |>
   mutate(made_shot = if_else(made_shot == "TRUE", 1, 0)) |>
   filter(made_shot == 1) |>
   group_by(shooting_team) |>
   summarise(shots_made = n())

 shots_taken_data <- end_of_game_shots |>
   group_by(shooting_team) |>
   summarise(shots_taken = n())

 temp_data <- left_join(shots_taken_data, shots_made_data)

 temp_data[is.na(temp_data)] <- 0

 shooting_percentage <- temp_data |>
   mutate(shot_percentage = round(shots_made / shots_taken, 3),
          total_shots = shots_taken + shots_made)

 shooting_percentage
```


shots_made_data1 |>
  ggplot(aes(x = fct_rev(fct_infreq(home)), fill =
made_shot)) + geom_bar(color = "black") +
theme(axis.text.x=element_text(angle=45, hjust=0.9)) +
scale_fill_manual(values = c("#E77500", "white")) + coord_flip() +
labs(title = "Shots Made vs. Missed Per WNBA Team", x = "WNBA Team", y =
"Number of Shots" )



## Graph For Shooting Percentage of WNBA Teams In Final 30 Seconds of Close Games

```{r}
shooting_percentage |> 
  ggplot(aes(x = reorder(shooting_team, shot_percentage), y = shot_percentage, fill = shooting_team)) +
  geom_bar(stat = "identity") +
   scale_fill_manual(values = c("#C8102E", "#418FDE", "#643335", "#C4D600", "#FFCD00", "#000000", "#702F8A", "#236192", "#003DA5","#CB6015","#2C5234", "#0C2340")) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=45, hjust=0.9)) +
  coord_flip() 
```

# Final Possession

## Games With Close Scores (3 points or less) Down To The Final Possession

```{r}
final_possession <- wnba_shots |> 
  group_by(game_id) |> 
  slice_max(game_play_number) |> 
  filter(score_differential %in% c(-3, -2, -1, 0, 1, 2, 3))

final_possession
```

## Number of Times Home Team In Close Game

```{r}
home_team_in_close_games <- final_possession |> 
  group_by(game_id) |> 
  slice_head() |> 
  group_by(home_team_name) |> 
  summarise(num_times_home = n()) |> 
  rename(team_name = home_team_name)

home_team_in_close_games
```

## Number of Times Away Team In Close Game

```{r}
away_team_in_close_games <- final_possession |> 
  group_by(game_id) |> 
  slice_head() |> 
  group_by(away_team_name) |> 
  summarise(num_times_away = n()) |> 
  rename(team_name = away_team_name)

away_team_in_close_games
```

```{r}
close_game_appereances <- full_join(away_team_in_close_games, home_team_in_close_games)



close_game_appereances[is.na(close_game_appereances)] <- 0

close_game_appearances <- close_game_appereances |> 
  mutate(num_close_games = num_times_away + num_times_home)

close_game_appearances
```

## Number of Games That Came Down To Final Possession Per Team

```{r}
ggplot(close_game_appearances, aes(x = reorder(team_name, num_close_games), y = num_close_games, fill = team_name)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("#C8102E", "#418FDE", "#643335", "#C4D600", "#FFCD00", "#000000", "#702F8A", "#236192", "#003DA5","#CB6015","#2C5234", "#0C2340")) +
  coord_flip()
```

## Number of Home vs. Away Games That Came Down To Final Possession Per Team

```{r}

close_game_appearances2 <- close_game_appearances |> 
  select(!num_close_games)

library(reshape2)
df_long <- melt(close_game_appearances2)

df_long

# To Match Previous Styles
ggplot(df_long, aes(x = team_name, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.9)) +
  scale_fill_manual(values = c("white", "#E77500")) +
  coord_flip()

# New Style
ggplot(df_long, aes(x = team_name, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.9)) +
  scale_fill_manual(values = c("white", "#E77500")) 

```

## Teams Who Shot Best In Close Games That Came Down To The Final Possession

```{r}
final_shots_made_data <- final_possession |>
  mutate(made_shot = if_else(made_shot == "TRUE", 1, 0)) |> 
  filter(made_shot == 1) |> 
  group_by(shooting_team) |> 
  summarise(shots_made = n())

final_shots_taken_data <- final_possession |>
  group_by(shooting_team) |> 
  summarise(shots_taken = n()) 
 
temp_data_2 <- left_join(final_shots_taken_data, final_shots_made_data)

temp_data_2[is.na(temp_data_2)] <- 0

final_shooting_percentage <- temp_data_2 |> 
  mutate(shot_percentage = round(shots_made / shots_taken, 3))  

final_shooting_percentage
```

## Number of Shots That Came Down To Final Possession Per Team (Does Not Include Teams With 0)

```{r}
ggplot(final_possession, aes(x = fct_rev(fct_infreq(shooting_team)), fill = shooting_team)) +
  geom_bar() +
  coord_flip() +
  scale_fill_manual(values = c("#C8102E", "#418FDE", "#C4D600", "#FFCD00", "#702F8A",  "#003DA5","#CB6015", "#2C5234", "#0C2340"  )) 
  # scale_color_manual(values = c("#418FDE", "#FFCD00", "#0C2340", "#041E42", "#FFC72C", "#FF671F", "#201747", "#FBE122", "#C8102E"))
```

