---
title: "WNBA Eda Project - Belle Schmidt"
output: html_document
date: "2024-06-06"
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
wnba_shots <- read_csv("https://raw.githubusercontent.com/36-SURE/36-SURE.github.io/main/data/wnba_shots.csv")

#View(wnba_shots)
```

# Removed The All Star Game & Added Shooter Variable
```{r}
wnba_shots <- wnba_shots |>
  filter(shooting_team != "Team Stewart" & shooting_team != "Team Wilson") |> 
  mutate(shooter_first_name = word(desc, 1),
         shooter_last_name = word(desc, 2),
         shooter = paste(shooter_first_name, shooter_last_name),
         score_differential = home_score - away_score) |>
  select(! c(shooter_first_name, shooter_last_name))

#View(wnba_shots)
```


# Overarching Question - How does time left in the game impact each team's performance? 


## Shooting in the last 2 minutes of the Second Quarter

```{r}
wnba_shots |>
  filter(qtr == 2 & quarter_seconds_remaining <= 120.0) |>
  arrange(quarter_seconds_remaining)
```


## Shooting in the last 2 minutes of the Fourth Quarter
```{r}
wnba_shots |>
  filter(qtr == 4 & quarter_seconds_remaining <= 120.0) |>
  arrange(quarter_seconds_remaining)
```
# Last Thirty Seconds

## Games With Close Scores (6 points or less) In The Last 30 Seconds
```{r}
end_of_game_shots <- wnba_shots |>
  filter(game_seconds_remaining < 30 & score_differential %in% c(-6, -5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6)) 

num_games <- end_of_game_shots |> 
  group_by(game_id) |> 
  slice_head() 
  
  
```


## Number of Shots In The Last 30 Seconds Per Close Game
```{r}
 end_of_game_shots |> 
  count(game_id) |> 
  arrange(-n)
```

## Teams Who Shot Best In Close Games (30 Seconds)
```{r}
shots_made_data1 <- end_of_game_shots |>
   mutate(made_shot = if_else(made_shot == "TRUE", "Made", "Missed")) 

 shots_made_data1

 shots_made_data <- end_of_game_shots |>
   mutate(made_shot = if_else(made_shot == "TRUE", 1, 0)) |>
   filter(made_shot == 1) |>
   group_by(shooting_team) |>
   summarise(shots_made = n())

 shots_made_data

 shots_taken_data <- end_of_game_shots |>
   group_by(shooting_team) |>
   summarise(shots_taken = n())

 temp_data <- left_join(shots_taken_data, shots_made_data)

 temp_data[is.na(temp_data)] <- 0

 shooting_percentage <- temp_data |>
   mutate(shot_percentage = round(shots_made / shots_taken, 3))

 shooting_percentage
```
## Number of Games That Came Down To Final Possession Per Team (Does Not Include Teams With 0)

```{r}
ggplot(end_of_game_shots, aes(x = shooting_team, fill = shooting_team)) +
  geom_bar() +
  coord_flip() + 
  scale_fill_manual(values = c("#C8102E", "#418FDE", "#643335", "#C4D600", "#FFCD00", "#000000", "#702F8A", "#236192", "#003DA5","#CB6015","#2C5234", "#0C2340")) 
  
```

## Graph For Shooting Percentage of WNBA Teams In Final 30 Seconds of Close Games

```{r}
shots_made_data1 |> 
  ggplot(aes(x = shooting_team, fill = made_shot)) +
  geom_bar() +
  theme_bw() +
   theme(axis.text.x=element_text(angle=45, hjust=0.9)) 
```


## Graph For Shooting Percentage of WNBA Teams In Final 30 Seconds of Close Games

```{r}
shooting_percentage |> 
  ggplot(aes(x = reorder(shooting_team, shot_percentage), y = shot_percentage, fill = shooting_team)) +
  geom_bar(stat = "identity") +
   scale_fill_manual(values = c("#C8102E", "#418FDE", "#643335", "#C4D600", "#FFCD00", "#000000", "#702F8A", "#236192", "#003DA5","#CB6015","#2C5234", "#0C2340")) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=45, hjust=0.9)) +
  coord_flip() 
```

# Final Possession

## Games With Close Scores (3 points or less) Down To The Final Possession
```{r}
final_possession <- wnba_shots |> 
  group_by(game_id) |> 
  slice_max(game_play_number) |> 
  filter(score_differential %in% c(-3, -2, -1, 0, 1, 2, 3))

final_possession
```

## Number of Times Home Team In Close Game 
```{r}
home_team_in_close_games <- final_possession |> 
  group_by(game_id) |> 
  slice_head() |> 
  group_by(home_team_name) |> 
  summarise(num_times_home = n()) |> 
  rename(team_name = home_team_name)

home_team_in_close_games
```

## Number of Times Away Team In Close Game 
```{r}
away_team_in_close_games <- final_possession |> 
  group_by(game_id) |> 
  slice_head() |> 
  group_by(away_team_name) |> 
  summarise(num_times_away = n()) |> 
  rename(team_name = away_team_name)

away_team_in_close_games
```


```{r}
close_game_appereances <- full_join(away_team_in_close_games, home_team_in_close_games)



close_game_appereances[is.na(close_game_appereances)] <- 0

close_game_appearances <- close_game_appereances |> 
  mutate(num_close_games = num_times_away + num_times_home)

close_game_appearances
```


## Number of Games That Came Down To Final Possession Per Team 
```{r}
ggplot(close_game_appearances, aes(x = reorder(team_name, num_close_games), y = num_close_games, fill = team_name)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("#C8102E", "#418FDE", "#643335", "#C4D600", "#FFCD00", "#000000", "#702F8A", "#236192", "#003DA5","#CB6015","#2C5234", "#0C2340")) +
  coord_flip()
```
## Number of Home vs. Away Games That Came Down To Final Possession Per Team 
```{r}

close_game_appearances2 <- close_game_appearances |> 
  select(!num_close_games)

library(reshape2)
df_long <- melt(close_game_appearances2)
ggplot(df_long, aes(team_name, value, fill = variable))+
     geom_bar(stat="identity", position="dodge") +
  theme_bw() +
  theme(axis.text.x=element_text(angle=45, hjust=0.9)) +
  scale_fill_manual(values = c("lightblue", "pink"))
```

## Teams Who Shot Best In Close Games That Came Down To The Final Possession
```{r}
final_shots_made_data <- final_possession |>
  mutate(made_shot = if_else(made_shot == "TRUE", 1, 0)) |> 
  filter(made_shot == 1) |> 
  group_by(shooting_team) |> 
  summarise(shots_made = n())

final_shots_taken_data <- final_possession |>
  group_by(shooting_team) |> 
  summarise(shots_taken = n()) 
 
temp_data_2 <- left_join(final_shots_taken_data, final_shots_made_data)

temp_data_2[is.na(temp_data_2)] <- 0

final_shooting_percentage <- temp_data_2 |> 
  mutate(shot_percentage = round(shots_made / shots_taken, 3))  

final_shooting_percentage
```


## Number of Shots That Came Down To Final Possession Per Team (Does Not Include Teams With 0)

```{r}
ggplot(final_possession, aes(x = shooting_team, fill = shooting_team)) +
  geom_bar() +
  coord_flip() +
  scale_fill_manual(values = c("#C8102E", "#418FDE", "#C4D600", "#FFCD00", "#702F8A",  "#003DA5","#CB6015", "#2C5234", "#0C2340"  )) 
  # scale_color_manual(values = c("#418FDE", "#FFCD00", "#0C2340", "#041E42", "#FFC72C", "#FF671F", "#201747", "#FBE122", "#C8102E"))
```
