---
title: "R Shiny App"
author: "Belle Schmidt"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: 
      version: 4
      bootswatch: sandstone
---

About
==========================


### **Additional Information:** 

**Authors:**

Belle Schmidt, Liam Jennings, and Cole Siniawski


**Objective:**

Although we outlined a few questions, our shiny app gives viewers the flexibility to look at many different questions regarding the WNBA. We hope that viewers may be able to learn more about the best teams and players and be able to find similarities and differences between the best and the worst.


**Tribulations and Victories of Data Acquisition and Wrangling:**




**Color Scheme:**




### **Defining The Variables**

```{r global, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(flexdashboard)
#library(shinydashboard)
library(shiny)
library(bslib)
theme_set(theme_bw())
wnba_shots <- read_csv("https://raw.githubusercontent.com/36-SURE/36-SURE.github.io/main/data/wnba_shots.csv")

#View(wnba_shots)
```


```{r, echo = FALSE}
# Removed The All Star Game & Added New Variables
wnba_shots <- wnba_shots |>
  filter(shooting_team != "Team Stewart" & shooting_team != "Team Wilson") |> 
   mutate(shooting_player = ifelse(
      str_detect(desc, "blocks") == TRUE,
      sub(".*?\\b(?:blocks)\\W+(\\w+(?:\\W+\\w+){0,2})\\b(?:'s| 's| B. 's)\\s.*", "\\1", desc, perl = TRUE), sub("\\ makes.*|\\ misses.*|\\ B. makes.*|\\ B. misses.*", "\\1", desc)),
         score_differential = home_score - away_score, 
         free_throw = if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 3 of"), 3,
       if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 2 of"), 2,
               if_else(str_detect(shot_type, "[Ff]ree [Tt]hrow - 1 of") | str_detect(shot_type, "[Tt]echnical"), 1, 0))),
       made_shot = if_else(made_shot == "TRUE", "Made", "Missed"),
       Shooting_Team_Home_Away = if_else(shooting_team == home_team_name, "Home", "Away"))
  
  

#View(wnba_shots)
```

```{r, echo = FALSE}
# Shots taken in the last 30 seconds of the fourth quarter Where the score differential was less than 6 after the shot was taken
end_of_game_shots <- wnba_shots |>
  filter(game_seconds_remaining <= 30 & score_differential %in% c(-6, -5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6) & qtr == 4) 

# All Close Games
all_close_games <- end_of_game_shots|> 
  distinct(game_id) 

# All Shots Taken In Last 30 Seconds 
all_shots <- wnba_shots|>
  filter(game_seconds_remaining <= 30 & qtr == 4) 
  
# All Shots Taken In Last 30 Seconds In Close Games
all_close_game_shots <- left_join(all_close_games, all_shots) |> 
  mutate(made_shot = factor(made_shot,levels = c("Missed", "Made"))) 


# The earliest time within the last 30 seconds where a shot occurred for a close game
close_games <- end_of_game_shots |> 
  group_by(game_id) |> 
  slice_max(game_seconds_remaining) |> 
  arrange(-free_throw) |> 
  slice_head() |> 
  select(game_id, home_team_name, away_team_name, score_differential) 


# The score after the last shot of every game 
final_score <- wnba_shots |> 
  group_by(game_id) |> 
  slice_min(game_seconds_remaining) |> 
  arrange(free_throw) |> 
  slice_head() |> 
   rename(final_score_differential = score_differential) |> 
   select(game_id, final_score_differential) 

# Score Change From First Shot In Last 30 Seconds To Last Shot of Game & Final Outcomes Added
close_games_observing <- left_join(close_games, final_score) |> 
  mutate(home_team_outcome =  
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential == final_score_differential, "Won - Kept Same Lead",
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential > final_score_differential, "Won - Lead Decreased",
 if_else(score_differential > 0 & final_score_differential > 0, "Won - Extended Lead",
 if_else(score_differential > 0 & final_score_differential == 0, "Tied - Lost Lead", 
 if_else(score_differential > 0 & final_score_differential < 0, "Lost - Lost Lead", 
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential == final_score_differential, "Lost - No Comeback",
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential > final_score_differential, "Lost - Deficit Increased",
 if_else(score_differential < 0 & final_score_differential < 0 & final_score_differential > score_differential, "Lost - Deficit Decreased",
 if_else(score_differential < 0 & final_score_differential == 0, "Tied - Comeback",
 if_else(score_differential == 0 & final_score_differential == 0, "Tied - No Change",
 if_else(score_differential == 0 & final_score_differential > 0, "Won - From Tie",
 if_else(score_differential == 0 & final_score_differential < 0, "Lost - From Tie", 
         "Won - Took Lead From Loss")))))))))))),
 away_team_outcome =  
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential == final_score_differential, "Lost - No Comeback",
 if_else(score_differential > 0 & final_score_differential > 0 & score_differential > final_score_differential, "Lost - Deficit Decreased",
 if_else(score_differential > 0 & final_score_differential > 0, "Lost - Deficit Increased",
 if_else(score_differential > 0 & final_score_differential == 0, "Tied - Comeback", 
 if_else(score_differential > 0 & final_score_differential < 0, "Won - Took Lead From Loss", 
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential == final_score_differential, "Won - Kept Same Lead",
 if_else(score_differential < 0 & final_score_differential < 0 & score_differential > final_score_differential, "Won - Extended Lead",
 if_else(score_differential < 0 & final_score_differential < 0 & final_score_differential > score_differential, "Won - Lead Decreased",
 if_else(score_differential < 0 & final_score_differential == 0, "Tied - Lost Lead",
 if_else(score_differential == 0 & final_score_differential == 0, "Tied - No Change",
 if_else(score_differential == 0 & final_score_differential > 0, "Lost - From Tie",
 if_else(score_differential == 0 & final_score_differential < 0, "Won - From Tie", 
         "Lost - Lost Lead")))))))))))),
 Home_Result = if_else(str_detect(home_team_outcome, "^Won"), "Win",
                       if_else(str_detect(home_team_outcome, "^Lost"), "Loss", "Tie")),
         Away_Result = if_else(str_detect(away_team_outcome, "^Won"), "Win",
                       if_else(str_detect(away_team_outcome, "^Lost"), "Loss", "Tie")))|> 
  ungroup() |> 
  mutate(away_team_outcome = factor(away_team_outcome, levels = c("Lost - Lost Lead", "Lost - Deficit Increased", "Lost - No Comeback", "Lost - Deficit Decreased", "Lost - From Tie", "Tied - Lost Lead", "Tied - No Change", "Tied - Comeback", "Won - Lead Decreased", "Won - Kept Same Lead", "Won - Extended Lead", "Won - From Tie", "Won - Took Lead From Loss")),
         home_team_outcome =factor(home_team_outcome, levels = c("Lost - Lost Lead", "Lost - Deficit Increased", "Lost - No Comeback", "Lost - Deficit Decreased", "Lost - From Tie", "Tied - Lost Lead", "Tied - No Change", "Tied - Comeback", "Won - Lead Decreased", "Won - Kept Same Lead", "Won - Extended Lead", "Won - From Tie", "Won - Took Lead From Loss")))


win_loss_color_vector <- c("Lost - Lost Lead" = "firebrick4", "Lost - Deficit Increased" = "firebrick", "Lost - No Comeback" = "firebrick3", "Lost - Deficit Decreased" = "firebrick2", "Lost - From Tie" = "firebrick1", "Tied - Lost Lead" = "darkorange1", "Tied - No Change" = "goldenrod1", "Tied - Comeback" = "gold", "Won - Lead Decreased" = "lightgreen", "Won - Kept Same Lead" = "green1", "Won - Extended Lead" = "green3", "Won - From Tie" = "green4", "Won - Took Lead From Loss" = "darkgreen")

```

League Performance In Close Home vs Away Games
==================================================

### Overarching Question 1 - How Does The League Overall Perform in Close Home Games Compared To Close Away Games?

Row
-------------------------------------

```{r, include=FALSE}
# Both Away And Home Win vs. Loss In League
win_losses <- close_games_observing |>
  pivot_longer(Home_Result:Away_Result,
               values_to = "win_or_loss",
               names_to = "home_or_away_result") |> 
  mutate(home_or_away_result = ifelse(home_or_away_result == "Home_Result", "Home", "Away"))
         
win_losses
```

```{r}
# Home vs. Away Outcomes 
league_win_vs_losses <- ggplot(win_losses, aes(x = home_or_away_result, fill = win_or_loss)) +
  geom_bar(position = position_fill()) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("firebrick", "goldenrod1", "green4")) +
  labs(title = "Outcomes For Home And Away Teams In Close Games",
       x = "Home vs. Away",
       fill = "Result") 


league_win_vs_losses
```

```{r, include=FALSE}

# Home Team Results By League
num_home_outcomes <- close_games_observing |>
  select(home_team_outcome, Home_Result) |> 
  count(home_team_outcome, Home_Result) |> 
  rename(num_times_home = n,
         outcome = home_team_outcome)

# Away Team Results By League
num_away_outcomes <- close_games_observing |>
  select(away_team_outcome, Away_Result) |> 
  count(away_team_outcome, Away_Result) |> 
  rename(num_times_away = n,
         outcome = away_team_outcome) 

#num_away_outcomes


# Number of Occurences of All Outcomes For Home vs. Away
possible_outcomes <- full_join(num_home_outcomes, num_away_outcomes, by = "outcome") |> 
  mutate(num_times_home = replace_na(num_times_home, 0),
         num_times_away = replace_na(num_times_away, 0),
         Win_Loss = ifelse(is.na(Away_Result), Home_Result, Away_Result)) |> 
  select(-Home_Result, -Away_Result)

#possible_outcomes
```

```{r}
# Home Outcome Types Occured Across Leagues In Close Games

home_outcomes <- ggplot(possible_outcomes, aes(x = Win_Loss, y = num_times_home, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Occurences of Each Outcome Type For Home Teams",
       y = "Occurences",
       fill = "Outcome") +
  scale_fill_manual(values = win_loss_color_vector) +
  theme(axis.title.x = element_blank()) 



# Away Outcome Types Occured Across Leagues In Close Games
away_outcomes <- ggplot(possible_outcomes, aes(x = Win_Loss, y = num_times_away, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Occurences of Each Outcome Type For Away Teams",
       y = "Occurences",
       fill = "Outcome") +
  scale_fill_manual(values = win_loss_color_vector)+
  theme(axis.title.x = element_blank()) 

# Combined Graph of Away vs Home Team Outcomes; Point Out Away Teams Win More In Close Games
library(patchwork)

away_outcomes + home_outcomes +
  plot_layout(guides = "collect", nrow = 2) +
  labs("Occurences Of Each Outcome Type For Both Home and Away Teams In Close Games")
```

```{r}
  ggplot(all_close_game_shots, aes(x = Shooting_Team_Home_Away)) +
  geom_bar(aes(fill = made_shot), color = "black", position = "fill") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("white", "#E77500")) +
  labs(title = "Shooting Percentage For Home And Away Teams In Close Games",
       x = "Home vs. Away",
       fill = "Result") +
  theme_gray()
```

